---
title: "SMI205 Replication Project"
author: '200382074'
date: "May 2024 (Academic Year 2024 ~ 2025)"
output:
  rmdformats::html_clean:
    code_download: yes
    toc: yes
    toc_depth: 2
    toc_float: True

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Classroom defending norms in victims casual attributes and social comparisons.

### R-Pubs Link :
# Replicated Paper

This project is based on the following paper:

**The Longitudinal role of classroom defending norms in victims psychological adjustments, casual attributes and social comparisons.**

Laninga-Wijnen, L., Garandeau, C. F., Malamut, S. T., & Salmivalli, C. 

Publishing dates: Recieved October 2022, Accepted July 2023 & first published October 2023 in the Developmental Psychology, 60(3), 522–544.

*DOI APA PsychNet:* https://doi.org/10.1037/dev0001629

## Workspace setup 

***Workspace setup*** 

```{r packages, message=FALSE, warning=FALSE}
#calling relevant libraries 
library(haven)
library(knitr) 
library(devtools)
library(summarytools)
library(lme4)
library(sjPlot)
library(Matrix)
```
Below is my YAML setup 



# 1. Introduction 

***Introduction***

- Critical & evidence based reflection on the original paper + new research questions that i have created.

# 2.Data & Methods 

## 2.1. Data 

**Dataset:** The idea was taken from challenge project which aimed at identifying bullying causes in Finnish schools. The data set is private and accessible via emailing the author as the students are under 18 therefore private information is kept secure (~ find policy around this). 

**Year:** 2020-2021, 3 waves but for this study we looked at wave 1 & 2

**Location:** Finland

**Population:** Finnish Elementary & Secondary school students

**Type of dataset:** Privatised (received from the author) 

**Number of observations:** 3500 


- Descriptive tables 
- The data used - how it was manipulated and variables 
 
 
## 2.2. Methods 

- transparency of altered data and analysis of the new theory 


# 3. Results 

- code and all graphs/tables (original and improved)
- Be transparent - from original tables/graphs to new ones


# 4. Conclusion 

- summaries whats found
- transparency of evidence found/used 
- Limitations of project (is there a gap in literature & any need for further research)


# 5. References 
***Main Paper:*** https://psycnet.apa.org/fulltext/2024-14052-001.html  

# 6. Appendix 1: Session Info


# 7. Appendix 2: R Script




