---
title: "SMI205_Preregistration_form"
author: "200382074"
date: "14/05/2024"
output: 
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
# By default, the code chunks are hidden. 
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages and data, message=FALSE, warning=FALSE}
library(skimr)
library(texreg)
library(broom.mixed)
library(lme4)
library(multilevelTools)
library(lmerTest)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(jtools)
library(broom)
library(dplyr)
library(QuantPsyc)
library(tidyverse)
library(ggplot2)
library(haven)
library(Matrix)
library(readxl)
library(readr)
library(janitor)
```

```{r data}
data <- read_excel("C:/Users/User/Downloads/Rproj/Rproj/data/data with headings.xlsx") 
```

# 1. My replication project
What is the paper?
The paper examines If there is a link between victimisation and psychological adjustments was moderated by classroom defending norms through use of longitudinal designs. This topic was looked at because it aimed to explain why defending norms either has beneficial or adverse effects on victims adjustments. This research was carried out by focusing on two cognitive processes, which are victims casual attributes and social comparisons, these are used in how peers cope in stressful events – in this case victimisation. 

Before looking at the data, the study currently indicates that many victims do not appear to gain from being in a classroom that has a high defending norm. But stable victims may have more of a psychological problem in high defending norms. 

Results
The results indicate that encouraging peers to defend victimised classmates may not be enough to help victims. The interclass correlation carried out shows that majority of the variance was due to differences between each other rather than the classrooms. 

Finally, the data showed that classrooms do have a norm and that higher victimisation was believed to be associated with higher self-blame and bully-blame plus, had worse psychological adjustments. 

DOI: https://doi.org/10.1037/dev0001629 


This is a preregistration of an extension project for the following study:

> Reference the chosen paper for your project here

In my replication project I am focusing on the following argument made in the study:

- Claim 3: page 6 <-  To examine the moderating role of defending norms in the link between victimization and psychological adjustment, additional analyses in which we examined the series of models described above separately for bully-directed defending norms and victim-directed defending norms.

- Table 3:page 10

# 2. Planned project extention

## 2.1. Rationale for a new hypothesis
I want to take apart the original claim and separate into two different hypothesis, because the model to me was more complicated and didn't really give a clear result to the question being asked. So by focusing on one effect of the type of blame may give a better result. My aim is to see what age bullying increases/starts at and which gender is more likely to get bullied. This then leads to me looking at how likely someone is to stand up to someone being bullied depending on who they blame for the bullying. 

By looking at these variables separately and tested in this way, i want to go down the route of looking at maturity in students through use of the grade that they are in, and if blame type alters through age groups. 

Claim - 1. Does the view of self blame/bully blame affects chances of pupils defending norms.
2. Is the victimisation rate different across the Grades and between Genders 

## 2.2. Prediction
Similar to original claim of defending norms in the link between victimisation and psychological adjustment. However, i am wanting to take apart this as it seems too big to explain the link between victimisation, psychological adjustment against defending norms. 

The aim is to see if victimisation is altered with age (the more someone matures the more likely people get bullied) and if more girls than boys get bullied in schools. 

Next is by looking at defending norms separately there may be a clearer result and if self blame or bully blame prevents defending norms more or less than the other. 

So, the results i hope for is a clear difference of victimisation across the grades and genders, which backs up research and helps the original paper get an understanding of the start of where bullying begins. For the defending norms being affected by self blame or bully blame, i hope to get an understanding of if self blame effects chances of someone defending another due to them lacking confidence. whereas bully blame should be a little bit higher for defending norms because people will defend others as they have more understanding of how people act and more confidence if they do not blame themselves. Both self blame and bully blame will have a mental and physical toll on themselves which may cause anxiety or depression, however bully blame may be higher than self blame as they understand preventing the actions of the bully reduces victimisation. (i will use research to back up this point in the actual assignment.) 

> Hypothesis: 

Do you expect to get the same or  different results from the original study? Why?

# 3. Data
- Original_data - Original data without headings - consists of all data in the study
- data_with_headings - original data with headings - consists of all data in the study. 
- dataset - orignal data with headings - made smaller by only including the data i need for my models (defending norms,
victimisation, self blame, bully blame, Gender & Grade).

'dataset' will be created in the code and manipulated but 'original data' and 'data with headings' are already pre-made data saved onto my computer. 

# 4. Data analysis plan

## 4.1. Model specification

I will test the hypothesis using the different regression model applied in the Longitudinal role of classroom defending norms in victims psychological adjustments, casual attributes and social comparisons study. 

For the first change of the original claim - Does the view of self blame/bully blame affects chances of pupils defending norms. I will be using a linear regression because this shows how likely the type of blame effects defending norms.It will be shown as a table but final understanding will be using a scatter plot of the data. 

For the second change to the original claim - Is the victimisation rate different across the Grades and between Genders, I will just be doing a simple bar chart which tells victimisation levels across each grade and gender to see if victimisation increases as someone ages or if it differs due to the gender you are. 

## 4.2. Variables
The variables have been measured through a survey that was given to the students directly during class time and consisted of tick boxes that got peoples opinions on questions related to the research paper. The only questions manipulated other than removing missing data was the Grade variables by only looking at grades 4-9 and removing other grades, as these where the grades that consisted of the age groups wanted for the paper.

__Dependent variable(s):__
1. Victimisation 
2. Defending Norms 

__Independent variables (IVs):__

- Self Blame W2
- Bully Blame W2 
- Gender (0 = Female, 1 = Male)
- Grade (4-9)

## 4.3. Interference criteria
I will use the standard p<0.05 criteria for determining if the statistical tests suggest that the results are significantly significant for both claims. Confidence interval for the first claim of comparing defending norms to self blame and bully blame because if a result is in the 95% interval it has a 5% chance of being incorrect. 

## 4.4. Data exclusion
No checks will be performed other than verification that each respondent answered each of the survey questions. If not answered it is classed as missing data.

## 4.5. Missing data
If a respondent refuses to answer or skips the question then that observation will not be included in the analysis. It was be changed to a 0 or -9999 which then will be removed as these symbolise a Null answer.

## 4.6. Exploratory data anlysis
Not applicable 

# 5. Session info

This preregistration form was completed in the following R environment:

```{r session}
sessionInfo()
```

# 6. References

<!--
Original_data <- read_csv("Research Project/data/Challenge_3470_imputedEMvict2.dat") 
data_with_headings <- read_excel("Research Project/data/data with headings.xlsx")
-->

Bartlett J. (2021). [OSF preregistration template.Rmd ](https://github.com/BartlettJE/BartlettJE.github.io/blob/master/RMarkdown-scripts/OSF%20preregistration%20template.Rmd). GitHub (accessed 03/05/2023)

Bowman, S. D., DeHaven, A. C., Errington, T. M., Hardwicke, T. E., Mellor, D. T., Nosek, B. A., & Soderberg, C. K. (2020). OSF Prereg Template. https://doi.org/10.31222/osf.io/epgjd. OSF (accessed 03/05/2023)
